---
title: "BBM713 - Data Mining"
subtitle: "2021 Fall Final Project Report"
author: "Doç. Dr. Burkay Genç and Some Other Guy"
date: "due 05/01/2022"
output: 
  html_document: 
    toc: yes
    theme: journal
    number_sections: yes
    df_print: tibble
---

# Summary

Here we outline our project and explain our motivation in doing this project in one paragraph.

In every part of the below document, you should both include textual explanations (like this) and R code of your study:

```{r}
print("like this...")
```

Your code should be runnable. You should finally knit this document as a pdf file and submit the pdf file (only) at [this form](https://forms.gle/idXra1iXMeg8poUr6).


# Introduction

It is time to explain more about where the data comes from, why we are doing this, what are we expecting to achieve and whether there exists any related work in the literature. If the data is manually collected, then explain how. 




## Data Source

Data related things... Did you get it from somewhere, was it clean, or did you collect it yourself? Who is the owner, is it publicly available, etc.
If possible, leave a [link](some url) here where I can reach the raw data.


## Related Work
```{r}
print("There are some works which their prediction methods does notinclude machine learning methods.")
print("Perozzi et al. propose a wind estimation solution to help wind speed sensor.In the case wind sensor does not exist, or the wind sensor gives noisy outputs, they introduce an algorithm to compensate this void using inertial sensor data of quadrotors.")
print("Another research without using an extra anemometer sensor which measures wind speed is proposed by Neuman et al for micro UAVs. This model does not require any additional sensor.Hence, it enables making more lightweight micro UAVs for producers.Also it provides more position for payload and other possible sensors.")
print("Furthermore, there are some research which uses deep learning models. Allison et al. proposed a model utilizing pitch and roll values of small quadcopter as input values to LSTM networks to predict
wind velocities in a turbulent wind environments without ant wind sensor.")
```



# Preprocessing

Explain the steps of preprocessing you applied.

## Cleaning

## Imputation

## Anomaly detection

## Feature extraction

## Dimensionality reduction



# Methodology

Now that the data is ready for processing, how did you do it? Explain the models you used, the parameters you have chosen, and the results you obtained.

## Model training

## Evaluation of results


# Discussion

You should now discuss your results and derive a wisdom out of this study. 
