---
title: "BBM713 - Data Mining"
subtitle: "2021 Fall Final Project Report"
author: "Doç. Dr. Burkay Genç and Some Other Guy"
date: "due 05/01/2022"
output: 
  html_document: 
    toc: yes
    theme: journal
    number_sections: yes
    df_print: tibble
---

# Summary

```{r}
print("Wind speed prediction problem is determining instant airspeed without using any type of anemometers which are mechanical wind speed measurement devices. Deploying a anemometer in a drone,unmanned air vehicle, can give accurate results, it comes at extra requirements,though.Especially lightweight drones consists of  minimum number of parts with minimum weights.Thus, predicting wind speed without a wind sensor become important at this point.We investigated this problem via using kinematics sensor data,including velocity values for each x,y,z dimensions , acceleratation values , provided by on-board sensors on DJI Tello drone which is very lightweight drone.")

```

Your code should be runnable. You should finally knit this document as a pdf file and submit the pdf file (only) at [this form](https://forms.gle/idXra1iXMeg8poUr6).


# Introduction

It is time to explain more about where the data comes from, why we are doing this, what are we expecting to achieve and whether there exists any related work in the literature. If the data is manually collected, then explain how. 

## Data Source
<!-- Data related things... Did you get it from somewhere, was it clean, or did you collect it yourself? Who is the owner, is it publicly available, etc. If possible, leave a [link](some url) here where I can reach the raw data. -->
We collect our own data. Our data collection setup consists of 2 main component: 1) Drone with controller on phone. 2) anemometer. With this setup, we have 2 separate data stream during collection. 

We have [DJI Tello Drone](https://store.dji.com/product/tello?vid=38421) which is small and easy to use. Drone have various sensors and can be also used [programatically](https://github.com/dji-sdk/Tello-Python). We tried to move Drone programatically, however since it is not stable enough, we decided to move it manually. Available data to collect with Drone are pitch, roll, yaw, speeds of axis x/y/z, temperature, height, pressure, time, acceleration of axis x/y/z. Drone movement pipeline during data collection is given below:

1. Take off of the Drone
2. Moving te Drone forward approximately 10 meters
3. Bringing the Drone back in the same way
4. Going step 2 if there is enough charge else landing of the Drone

Another component of the setup is collecting wind speed data with an anemometer. We bought an [anemometre](https://www.trendyol.com/unit/uni-t-ut-363-mini-dijital-ruzgar-olcer-anemometre-p-56053867?boutiqueId=61&merchantId=218943) and a [tripod](https://www.trendyol.com/microcase/3-ayak-sabitleyici-aluminyum-cep-telefonu-kamera-dslr-led-light-tripodu-200-cm-al2630-p-110114864?boutiqueId=61&merchantId=108916) to collect wind data. We combine 2 data source by synchronizing time steps. However we have a challenging issue: different frequencies of each stream. Drone has ~24 fps, but frequency of anemometer is 1 sample per second. We explain how to handle this issue in pre-processing section.

### Step 1: Introducing Drone Data

```{r}
library(tidyr)
library(dplyr)
library(tibble)

set.seed(1024)


data_drone_path = "/home/emre/workspace/master/cmp713/project/data_final/data_drone.csv"
df_drone = as_tibble(read.csv(data_drone_path, header = TRUE))
head(df_drone, 10)
```

```{r summary of cols drone}

for(i in df_drone %>% names()) {       # for-loop over columns
  if (i == "timestamp"){
    next
  }
  
  cat("$", i, "\n", sep = "")
  print(summary(df_drone[[i]]))
  cat("\n")  
}

```

### Step 2: Introducing Wind Data

```{r}
data_wind_path = "/home/emre/workspace/master/cmp713/project/data_final/data_wind.csv"
df_wind = as_tibble(read.csv(data_wind_path, header = TRUE))
head(df_wind, 10)
```

```{r summary of cols wind}

for(i in df_wind %>% names()) {       # for-loop over columns
  if (i == "timestamp"){
    next
  }
  
  cat("$", i, "\n", sep = "")
  print(summary(df_wind[[i]]))
  cat("\n")  
}

```

### Step 3: Combining Two Data Source
Since frequencies of two stream are not same, when we combine streams, there was None values for some rows. For example if we got 20 Drone samples between 16:10:02- 16:10:03, we got only 1 wind sample. Hence we add combine these data by concating early Drone sample with Drone sample. Wind value of remaining samples of Drone data is set to "-1".
```{r}
df_path = "/home/emre/workspace/master/cmp713/project/data_final/combined.csv"
df = as_tibble(read.csv(df_path, header = TRUE))
head(df, 10)
```

### Step 4: Data Analysis and Relations
Since wind affects behaviour of Drone, we want to show relation between some features.

#### Wind Speed Histogram
:
```{r}
library(ggplot2) 

p1 <- ggplot(df, aes(x=wind.speed)) + geom_histogram(binwidth = 0.05) + xlab("windspeed")
p1
```

#### Height Histogram
:
```{r}
ggplot(df, aes(x=h)) + geom_histogram(binwidth=5) + xlab("h")
```

#### Speed Histograms
:
```{r}
library(gridExtra)

p1 <- ggplot(df, aes(x=vgx)) + geom_histogram(binwidth=5) + xlab("x")
p2 <- ggplot(df, aes(x=vgy)) + geom_histogram(binwidth=5) + xlab("y")
p3 <- ggplot(df, aes(x=vgz)) + geom_histogram(binwidth=5) + xlab("z")

grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

#### Acceleration Histograms
:
```{r}
p1 <- ggplot(df, aes(x=agx)) + geom_histogram(binwidth=5) + xlab("x")
p2 <- ggplot(df, aes(x=agy)) + geom_histogram(binwidth=5) + xlab("y")
p3 <- ggplot(df, aes(x=agz)) + geom_histogram(binwidth=50) + xlab("z")
df$agz
grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

#### Pitch/Roll/Yaw Histograms
:
```{r}
p1 <- ggplot(df, aes(x=pitch)) + geom_histogram(binwidth=1) + xlab("pitch")
p2 <- ggplot(df, aes(x=roll)) + geom_histogram(binwidth=1) + xlab("roll")
p3 <- ggplot(df, aes(x=yaw)) + geom_histogram(binwidth=1) + xlab("yaw")

grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

#### Relation between Wind Speed and pitch/roll/yaw
:
```{r}
p1 <- ggplot(df, aes(x=pitch, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=roll, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=yaw, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```

#### Relation between Wind Speed and Speeds
:
```{r}
p1 <- ggplot(df, aes(x=vgx, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=vgy, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=vgz, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```

#### Relation between Wind Speed and Accelerations
:
```{r}
p1 <- ggplot(df, aes(x=agx, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=agy, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=agz, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3), 
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```



## Related Work
```{r}
print("There are some works which their prediction methods does notinclude machine learning methods.")
print("Perozzi et al. propose a wind estimation solution to help wind speed sensor.In the case wind sensor does not exist, or the wind sensor gives noisy outputs, they introduce an algorithm to compensate this void using inertial sensor data of quadrotors.")
print("Another research without using an extra anemometer sensor which measures wind speed is proposed by Neuman et al for micro UAVs. This model does not require any additional sensor.Hence, it enables making more lightweight micro UAVs for producers.Also it provides more position for payload and other possible sensors.")
print("Furthermore, there are some research which uses deep learning models. Allison et al. proposed a model utilizing pitch and roll values of small quadcopter as input values to LSTM networks to predict
wind velocities in a turbulent wind environments without ant wind sensor.")
```



# Preprocessing

Explain the steps of preprocessing you applied.

## Cleaning

## Imputation

## Anomaly detection

## Feature extraction
```{r}
library(lubridate)

# Standardization expect timestamp, date, wind speed
df_mean <- apply(df[2:14], 2, mean)
apply(df[2:14], 2, range)
df_scaled <- cbind(df %>% select(timestamp), df %>% select(-timestamp) %>% select(-wind.speed) %>% scale(), df %>% select(wind.speed))
df_scaled
apply(df_scaled, 2, range)

df

df$h <- NULL
df
# Create Time Representations
# df$date = as_datetime(df$timestamp)
```


## Dimensionality reduction



# Methodology

Now that the data is ready for processing, how did you do it? Explain the models you used, the parameters you have chosen, and the results you obtained.

## Model training

## Evaluation of results


# Discussion

You should now discuss your results and derive a wisdom out of this study. 
