---
title: "BBM713 - Data Mining"
author: "Doç. Dr. Burkay Genç and Some Other Guy"
date: "due 05/01/2022"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    theme: journal
    number_sections: yes
    df_print: tibble
subtitle: 2021 Fall Final Project Report
---

\newpage
# Summary

```{r, results='asis'}
print("Wind speed prediction problem is determining instant airspeed without using any type of anemometers which are mechanical wind speed measurement devices. Deploying a anemometer in a drone, unmanned air vehicle, can give accurate results, it comes at extra requirements,though. Especially lightweight drones consists of  minimum number of parts with minimum weights. Thus, predicting wind speed without a wind sensor become important at this point. We investigated this problem via using kinematics sensor data, including velocity values for each x, y, z dimensions, acceleratation values, provided by on-board sensors on DJI Tello drone which is very lightweight drone.")

```

<!--Your code should be runnable. You should finally knit this document as a pdf file and submit the pdf file (only) at [this form](https://forms.gle/idXra1iXMeg8poUr6). -->


# Introduction

<!-- It is time to explain more about where the data comes from, why we are doing this, what are we expecting to achieve and whether there exists any related work in the literature. If the data is manually collected, then explain how. -->

## Data Source
<!-- Data related things... Did you get it from somewhere, was it clean, or did you collect it yourself? Who is the owner, is it publicly available, etc. If possible, leave a [link](some url) here where I can reach the raw data. -->
```{r, results='asis'}
print("We collect our own data. Our data collection setup consists of 2 main component: 1) Drone with controller on phone. 2) anemometer. With this setup, we have 2 separate data stream during collection.")

print("We have [DJI Tello Drone](https://store.dji.com/product/tello?vid=38421) which is small and easy to use. Drone have various sensors and can be also used [programatically](https://github.com/dji-sdk/Tello-Python). We tried to move Drone programatically, however since it is not stable enough, we decided to move it manually. Available data to collect with Drone are pitch, roll, yaw, speeds of axis x/y/z, temperature, height, pressure, time, acceleration of axis x/y/z. Drone movement pipeline during data collection is given below:")

print("1. Take off of the Drone")
print("2. Moving te Drone forward approximately 10 meters")
print("3. Bringing the Drone back in the same way")
print("4. Going step 2 if there is enough charge else landing of the Drone")

print("Another component of the setup is collecting wind speed data with an anemometer. We bought an [anemometre](https://www.trendyol.com/unit/uni-t-ut-363-mini-dijital-ruzgar-olcer-anemometre-p-56053867?boutiqueId=61&merchantId=218943) and a [tripod](https://www.trendyol.com/microcase/3-ayak-sabitleyici-aluminyum-cep-telefonu-kamera-dslr-led-light-tripodu-200-cm-al2630-p-110114864?boutiqueId=61&merchantId=108916) to collect wind data. We combine 2 data source by synchronizing time steps. However we have a challenging issue: different frequencies of each stream. Drone has ~24 fps, but frequency of anemometer is 1 sample per second. We explain how to handle this issue in pre-processing section.")
```

### Step 1: Introducing Drone Data

```{r}
library(tidyr)
library(dplyr)
library(tibble)

set.seed(1024)


data_drone_path = "C:/Users/User/Desktop/Drone-Wind-Prediction-main/Drone-Wind-Prediction-main/data/processed/data_drone.csv"
df_drone = as_tibble(read.csv(data_drone_path, header = TRUE))
head(df_drone, 10)
```

```{r summary of cols drone}

for(i in df_drone %>% names()) {       # for-loop over columns
  if (i == "timestamp"){
    next
  }

  cat("$", i, "\n", sep = "")
  print(summary(df_drone[[i]]))
  cat("\n")
}

```

### Step 2: Introducing Wind Data

```{r}
data_wind_path = "C:/Users/User/Desktop/Drone-Wind-Prediction-main/Drone-Wind-Prediction-main/data/processed/data_wind.csv"
df_wind = as_tibble(read.csv(data_wind_path, header = TRUE))
head(df_wind, 10)
```

```{r summary of cols wind}

for(i in df_wind %>% names()) {       # for-loop over columns
  if (i == "timestamp"){
    next
  }

  cat("$", i, "\n", sep = "")
  print(summary(df_wind[[i]]))
  cat("\n")
}

```

### Step 3: Combining Two Data Source
```{r, results='asis'}
print("Since frequencies of two stream are not same, when we combine streams, there was None values for some rows. For example if we got 20 Drone samples between 16:10:02- 16:10:03, we got only 1 wind sample. Hence we add combine these data by concating early Drone sample with Drone sample. Wind value of remaining samples of Drone data is set to '-1'.")
```

```{r}
df_path = "C:/Users/User/Desktop/Drone-Wind-Prediction-main/Drone-Wind-Prediction-main/data/processed/combined.csv"
df = as_tibble(read.csv(df_path, header = TRUE))
head(df, 10)
```

### Step 4: Data Analysis and Relations
```{r}
print("Since wind affects behaviour of Drone, we want to show relation between some features.")
```
\newpage

#### Wind Speed Histogram
:
```{r}
library(ggplot2)

ggplot(df, aes(x=wind.speed)) + geom_histogram(binwidth = 0.05) + xlab("windspeed")

```

\newpage
#### Height Histogram
:
```{r}
ggplot(df, aes(x=h)) + geom_histogram(binwidth=5) + xlab("h")
```

\newpage
#### Speed Histograms
:
```{r}
library(gridExtra)

p1 <- ggplot(df, aes(x=vgx)) + geom_histogram(binwidth=5) + xlab("x")
p2 <- ggplot(df, aes(x=vgy)) + geom_histogram(binwidth=5) + xlab("y")
p3 <- ggplot(df, aes(x=vgz)) + geom_histogram(binwidth=5) + xlab("z")

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

\newpage
#### Acceleration Histograms
:
```{r}
p1 <- ggplot(df, aes(x=agx)) + geom_histogram(binwidth=5) + xlab("x")
p2 <- ggplot(df, aes(x=agy)) + geom_histogram(binwidth=5) + xlab("y")
p3 <- ggplot(df, aes(x=agz)) + geom_histogram(binwidth=50) + xlab("z")

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

\newpage
#### Pitch/Roll/Yaw Histograms
:
```{r}
p1 <- ggplot(df, aes(x=pitch)) + geom_histogram(binwidth=1) + xlab("pitch")
p2 <- ggplot(df, aes(x=roll)) + geom_histogram(binwidth=1) + xlab("roll")
p3 <- ggplot(df, aes(x=yaw)) + geom_histogram(binwidth=1) + xlab("yaw")

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
```

\newpage
#### Relation between Wind Speed and pitch/roll/yaw
:
```{r}
p1 <- ggplot(df, aes(x=pitch, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=roll, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=yaw, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```

\newpage
#### Relation between Wind Speed and Speeds
:
```{r}
p1 <- ggplot(df, aes(x=vgx, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=vgy, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=vgz, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```

\newpage
#### Relation between Wind Speed and Accelerations
:
```{r}
p1 <- ggplot(df, aes(x=agx, y=wind.speed)) + geom_point()
p2 <- ggplot(df, aes(x=agy, y=wind.speed)) + geom_point()
p3 <- ggplot(df, aes(x=agz, y=wind.speed)) + geom_point()

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("axis x", "axis y", "axis z"),
            nrow=3)
# ggplot(df, aes(x=h, y=wind.speed, color=h_group)) + geom_point() + facet_wrap(~ h_group)
```


\newpage
## Related Work
```{r, results='asis'}
print("There are some works which their prediction methods does not include machine learning methods.")
print("Petrich et al. uses different sensors to estimate wind patterns for small UAVs.")
print("Perozzi et al. propose a wind estimation solution to help wind speed sensor.In the case wind sensor does not exist, or the wind sensor gives noisy outputs, they introduce an algorithm to compensate this void using inertial sensor data of quadrotors.")
print("Another research without using an extra anemometer sensor which measures wind speed is proposed by Neuman et al for micro UAVs. This model does not require any additional sensor.Hence, it enables making more lightweight micro UAVs for producers.Also it provides more position for payload and other possible sensors.")
print("Furthermore, there are some research which uses deep learning models. Allison et al. proposed a model utilizing pitch and roll values of small quadcopter as input values to LSTM networks to predict wind velocities in a turbulent wind environments without ant wind sensor.")
```


\newpage
# Preprocessing

<!-- Explain the steps of preprocessing you applied.-->

## Cleaning

```{r, results='asis'}
print("Since information of height is manually adjusted by us, it is not informative for decision of wind speed. Hence we remove it")
```

```{r}
df$h <- NULL
```

```{r, results='asis'}
print("We remove wind.speed=-1 samples from beginning and end since interpolation is not possible (explained in detail in the next section)")
```


```{r}
delete_index_first = 1
delete_index_last = nrow(df)

for(i in df$wind.speed) {       # for-loop over columns
  if (i == -1){
    delete_index_first = delete_index_first + 1
  }
  else{
    break
  }
}

for(i in nrow(df):1) {       # for-loop over columns
  if (df$wind.speed[i] == -1){
    delete_index_last = delete_index_last - 1
  }
  else{
    break
  }
}

df_clean = df[delete_index_first:delete_index_last, ]

```

```{r}
print("remained dataframe:")
df_clean
```

## Imputation
```{r, results='asis'}
print("We interpolate wind speed because of frequency mismatch.")
```


```{r}
library(zoo)

print(head(df_clean$wind.speed, 100))
df_clean$wind.speed[df_clean$wind.speed == -1] <- NA
df_clean$wind.speed <- na.approx(df_clean$wind.speed)
print(head(df_clean$wind.speed, 100))
```


## Anomaly detection

```{r, results='asis'}
print("")
```


```{r}

library(dplyr)
library(ggplot2)

library(cluster)
library(fpc)

library(dbscan)



outs <- function(data) {
  
  cl <- dbscan(data, eps=0.9, MinPts=5)
  posOuts <- which(cl$cluster == 0)
  list(positions = posOuts,
       outliers = data[posOuts,],
       dbscanResults = cl)
  }
dbscan.outliers <- outs(df_clean)

#print(dbscan.outliers$positions)

df_clean$outlier = 0
df_clean$outlier[df_clean$positions] = 1



```
\newpage
```{r}

p1 <- ggplot(df_clean, aes(
  x = vgx, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

p2 <-ggplot(df_clean, aes(
  x = vgy, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

p3 <- ggplot(df_clean, aes(
  x = vgz, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

grid.arrange(grobs = list(p1, p2, p3),
            labels = c("vgx", "vgy", "vgz"),
            nrow=3)


```
\newpage
```{r}

p4 <- ggplot(df_clean, aes(
  x = agx, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")


p5 <-ggplot(df_clean, aes(
  x = agy, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

p6 <-ggplot(df_clean, aes(
  x = agz, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

grid.arrange(grobs = list(p4, p5, p6),
            labels = c("agx", "agy", "agz"),
            nrow=3)

```
\newpage
```{r}

p7 <- ggplot(df_clean, aes(
  x = pitch, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")


p8 <- ggplot(df_clean, aes(
  x = roll, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

p9 <- ggplot(df_clean, aes(
  x = yaw, 
  y = wind.speed, 
  color = as.factor(outlier))) + 
  geom_point() + 
  theme(legend.position="bottom")

grid.arrange(grobs = list(p7, p8, p9),
            labels = c("pitch", "roll", "yaw"),
            nrow=3)
```
\newpage


## Feature extraction

```{r, results='asis'}
print("We apply standardization as a pre-preprocess")
```

```{r}
library(lubridate)

# Standardization expect time-stamp, wind speed
# df_clean_mean <- apply(df_clean[2:14], 2, mean)

print(apply(df_clean[2:14], 2, range))
df_clean_scaled <- cbind(df_clean %>% select(timestamp), df_clean %>% select(-timestamp) %>% select(-wind.speed) %>% scale(), df_clean %>% select(wind.speed))
print(apply(df_clean_scaled, 2, range))
```


## Dimensionality reduction

```{r, results='asis'}
print("We used correletion to observe if columns are related/informative or not. As we can see below, the least one is bat according to GainRatio. Hence we can remove it")
```

```{r}
library(rmarkdown) # used for syntax highlighting
library(knitr)
library(dplyr)
library(readr)
library(stringr)
library(lubridate)
library(xts)
library(sp)
library(CORElearn)

attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "GainRatio")
attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "InfGain")
attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "Gini")
attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "Relief")
attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "RReliefFequalK")
attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "MSEofMean")
# attrEval(wind.speed ~ ., df_clean_scaled %>% select(-timestamp), estimator = "MSEofModel")

df_clean_scaled$bat <- NULL
```

```{r, results='asis'}
print("We used PCA for dimensionality reduction.")
```

```{r}
df_clean_scaled$outlier <- NULL
pca <- princomp(df_clean_scaled %>% select(-timestamp))
loadings(pca)

new.df <- data.frame(pca$scores[, 1:10], wind.speed = df_clean_scaled$wind.speed)
head(new.df, 20)

```


# Methodology

Now that the data is ready for processing, how did you do it? Explain the models you used, the parameters you have chosen, and the results you obtained.
```{r, results='asis'}
print("We use three machine learning algorithms.These models are a decision tree,support vector machines(svm) and finally artificial neural network. ")

```

## Model training
```{r}
print("Train and test splitting is conducted.")
library(rpart)
library(rpart.plot)

library(caTools)

set.seed(101) 
sample = sample.split(new.df$wind.speed, SplitRatio = .75)
train = subset(new.df, sample == TRUE)
test  = subset(new.df, sample == FALSE)
print("Examples of Training Samples")
head(train, 5)
print("Examples of Test Samples")
head(test, 5)



```


```{r}
library(rpart)
library(rpart.plot)
library(mlbench)
library(DMwR2)
library(e1071)
library(performanceEstimation)
library(nnet)

nr <- nnet(wind.speed ~ ., train,
           linout=TRUE,
           trace=FALSE,
           size=4,
           decay=0.04,
           maxit=10)
psnr <- predict(nr, test)
mean(abs(psnr-test$wind.speed))

plt <- plot(as.vector(test$wind.speed), as.vector(psnr))
abline(0, 1)

```
```{r}
library(rpart)
library(rpart.plot)
library(mlbench)
library(DMwR2)
library(e1071)
library(performanceEstimation)
library(nnet)

nr <- nnet(wind.speed ~ ., train,
           linout=TRUE,
           trace=FALSE,
           size=4,
           decay=0.04,
           maxit=1000)
psnr <- predict(nr, test)
mean(abs(psnr-test$wind.speed))

plt <- plot(as.vector(test$wind.speed), as.vector(psnr))
abline(0, 1)

```
## Evaluation of results
```{r}
print("For nFold = 5")

r_svm <- performanceEstimation(
  PredTask(wind.speed ~ ., new.df),
  Workflow(learner = "svm"),
  EstimationTask(metrics = c("mse", "mae"),
                 method = CV(nReps = 8, nFolds = 5)))


summary(r_svm)

```
```{r}


r_decisiontree <- performanceEstimation(
  PredTask(wind.speed ~ ., new.df),
  Workflow(learner = "rpartXse"),
  EstimationTask(metrics = c("mse", "mae"),
                 method = CV(nReps = 8, nFolds = 5)))


summary(r_decisiontree)

```

\newpage
```{r}
print("We try nFold = 10")

r_svm <- performanceEstimation(
  PredTask(wind.speed ~ ., new.df),
  Workflow(learner = "svm"),
  EstimationTask(metrics = c("mse", "mae"),
                 method = CV(nReps = 8, nFolds = 10)))


summary(r_svm)

```
```{r}


r_decisiontree <- performanceEstimation(
  PredTask(wind.speed ~ ., new.df),
  Workflow(learner = "rpartXse"),
  EstimationTask(metrics = c("mse", "mae"),
                 method = CV(nReps = 8, nFolds = 10)))


summary(r_decisiontree)

```

# Discussion
```{r,results='asis'}

print("In this project, we experimented three different machine learning algorithms to estimate value of instant wind.
In order to measure our success for this prediction which is regression problem, we use two different metric which are mean squared error (mse) and mean absolute error(mae) and we mainly focus on mean absolute error.Collecting our data set manually with DJI tello drone, we created ,cleaned and conducted necessary arrangements in data set.It included noisy and unwanted parts but we removed them as possible as we can.After data set processing,  We trained decision tree and support vector machine using cross validation concept.
As we showed our mse and mae scores , conducting regression on this data set can be said as successful.To illustrate, artificial neural network model gives 0.002 mae error score which is 15 times better than support vector machine score 0.03 which is also good mae score.
When it comes to decision tree and svm scores, these two model gives very close mae scores to each other.")


```

# References
[1] Petrich, Jan, and Kamesh Subbarao. "On-board wind speed estimation for uavs." AIAA Guidance, Navigation, and Control Conference. 2011.
[2] Perozzi, Gabriele, et al. "Wind estimation algorithm for quadrotors using detailed aerodynamic coefficients." 2018 Annual American Control Conference (ACC). IEEE, 2018.
[3] Neumann, Patrick P., and Matthias Bartholmai. "Real-time wind estimation on a micro unmanned aerial vehicle using its inertial measurement unit." Sensors and Actuators A: Physical 235 (2015): 300-310.
[4] Allison, Sam, He Bai, and Balaji Jayaraman. "Wind estimation using quadcopter motion: A machine learning approach." Aerospace Science and Technology 98 (2020): 105699.
